\documentclass[twocolumn]{svjour3}
    

\usepackage{graphicx}      % include this line if your document contains figures
\usepackage{natbib}        % required for bibliography
\usepackage{enumerate}
\usepackage[utf8]{inputenc}
%\usepackage{float}
%\usepackage[centerlast,small,sc]{caption} 
%\setlength{\captionmargin}{30pt}
%\usepackage[none]{hyphenat} 
%\usepackage{subcaption} 
%\usepackage{capt-of}
%\usepackage{kpfonts}
%\usepackage{calc}
\newlength\shlength
\newcommand\xshlongvec[2][0]{\setlength\shlength{#1pt}%
  \stackengine{-5.6pt}{$#2$}{\smash{$\kern\shlength%
    \stackengine{7.55pt}{$\mathchar"017E$}%
      {\rule{\widthof{$#2$}}{.57pt}\kern.4pt}{O}{r}{F}{F}{L}\kern-\shlength$}}%
      {O}{c}{F}{T}{S}}
%\sloppy  
\journalname{Journal of Control, Automation and Electrical Systems}
\begin{document}

%\begin{frontmatter}

\title{State of the art and conceptual design of robotic solutions for
\textit{in situ} hard coating of hydraulic turbines}%\thanksref{footnoteinfo}} 



\author{Renan S. Freitas \and
		Gabriel Alcantara C. S. \and
		Eduardo Elael M. S. \and
		Estevão Fróes \and
		Ramon R. Costa}

\institute{Department of Electrical Engineering, COPPE
UFRJ, Rio de Janeiro, Brasil.
\email{renan028@gmail.com}}

\thanks{This work is supported by ESBR under contract COPPETEC
JIRAU 09/15 6631-0003/2015 (ANEEL R\&D program).}

\maketitle
  
\begin{abstract}      
Hydropower turbine's blades demand regular maintenance for flow stability and
turbine efficiency as they are constantly exposed to abrasion and cavitation
phenomena. Hard coating techniques by thermal aspersion are used to reduce the
erosion of the turbine's blade, thus increasing its life cycle. Currently,
blade's maintenance requires disassembling the turbine, and recalibration. EMMA
is an R\&D project of a robotic system to perform coating by thermal spray on
hydraulic turbine blades within the turbine environment. The project aims to
significantly reduce the downtime for hard coating process. This document
makes a survey of the state of the art of \textit{in situ} turbine systems, and
describes the conceptual designs for EMMA's robot and its
mechanical bases. The results outlines the next steps for EMMA and future
projects in the same area. 

\keywords{hard coating \and hydropower \and turbine \and thermal spray \and
robotics \and in situ}
\end{abstract} 

\input{Introduction} 
\input{Descricao}
\input{SOTA}
\input{Projetos}
\input{conclusao}

\bibliographystyle{spbasic}  
\bibliography{main} 
\end{document}
